%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.7in,top=0.5in,right=0.8in,bottom=0.5in]{geometry} % Document margins

\usepackage{xcolor}
\usepackage{url}
\usepackage[colorlinks,urlbordercolor=black,urlcolor=black]{hyperref}

\name{\Huge Q\huge izhou \Huge{Fang}} % Your name
%\address{Los Angeles} %
\address{15501 N Pennsylvania Ave, Edmond, OK 73013 $|$ (626) 313-8139 $|$  \href{mailto:qfang8ae@gmail.com}{\textcolor{black}{qfang8ae@gmail.com}}}
\address{\href{https://github.com/wsxxs2222}{\textcolor{black}{GitHub}} $|$ \href{https://www.linkedin.com/in/qizhou-fang-5932a9289}{\textcolor{black}{LinkedIn}}}
\begin{document}

	
	
	
	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
        \begin{rSection}{Work Experience}

            \begin{rSubsection}{\textbf{Android App Development Intern}}{Jan.2025 – July.2025}{YouVersion, Edmond, OK}{}
                \item Developed and maintained features for the \textit{Bible App Lite} Android application using Flutter and Dart, serving over 55 million users.
                \item Collaborated with product and design teams to implement new UI components and user flows.
            \end{rSubsection}
        
            \begin{rSubsection}{\textbf{Computer Fabrication Research Assistant}}{July 2023 – June 2024}{Davis, CA}{}
                \item Wrote Python and C++ scripts to simulate and generate 3D-printable microstructures for materials research.
            \end{rSubsection}
        
        \end{rSection}
 
	\begin{rSection}{Education}
		
		\begin{list}{$\bullet$}{\leftmargin=1em} % \cdot used for bullets, no indentation
			\itemsep -0.5em \vspace{0em} % Compress items in list together for aesthetics
			\item{
			{\bf University of California, Davis} \hfill\textit{Dec.2024} \\
			Master of Science, Computer Science \\
            \textit{Related Courses: Machine Learning \& Discovery, Advanced Machine Learning} \\
            \vspace{-0.5em}
		}

			\item{{\bf University of California, Irvine} \hfill\textit {Sep.2022} \\
				Bachelor of Science, Mathematics, Concentration in Data Science\\
				\vspace{-0.5em}\small
			}
			
		\end{list}
	\end{rSection}
	
	\begin{rSection}{Projects}

        \begin{rSubsection}{\bf Bible App Lite – “Get Help” Feature Redesign (YouVersion Internship)}{Mar.2025 - June.2025}{}{}
             \item {Integrated real-time customer support via WhatsApp and SMS, increasing user accessibility and satisfaction through familiar messaging platforms.}
             \item {Designed client-side caching and refresh logic to store and update support contact data efficiently.}
             \item {Streamlined the ``Get Help" experience by optimizing API interactions, leading to reduced user friction and faster access to support resources.}
        \end{rSubsection}

        \begin{rSubsection}{\bf Microstructure Design Automation for Target Elasticity \href{https://docs.google.com/presentation/d/1vE1fTo60TzdEpiMjofUK8VLwj55keTxsokcQTI54zJE/edit?usp=sharing}{[Slides]}}{July 2023 -- June 2024}{}{}
            \item{Modeled the microstructure optimization task as a loss minimization problem to match target elasticity properties using SciPy.}
            \item{Improved custom C++ linear solvers to handle periodic boundary conditions, reducing computation time by 41\%.}
            \item{Evaluated and compared multiple loss functions to improve convergence and accuracy of generated microstructures.}
        \end{rSubsection}

        \begin{rSubsection}{\bf IBlog – Full-Stack Blog Platform \href{https://github.com/JaekeeAI/ecs162finalproject}{[GitHub]}}{May.2024 - June.2024}{}{}
             \item{Built a blog platform using Handlebars for server-side rendering and JavaScript for dynamic client interactions.}
             \item{Implemented RESTful APIs to manage user accounts and blog posts using a SQLite database.}
             \item{Added search and sort functionality to enhance user experience and content discoverability.}
        \end{rSubsection}
            
        \begin{rSubsection}{\bf Pygame Chess UI – Standard + Fog of War Mode\href{https://github.com/wsxxs2222/chess_game}{[GitHub]}}{July 2023 -- March 2024}{}{ }
            \item{Created a custom graphical chess interface using Pygame with piece animations and event handling.}
            \item{Developed LAN multiplayer using Python sockets to support both standard and Fog of War chess variants across multiple devices.}
        \end{rSubsection}
    
        \begin{rSubsection}{\bf AI-Based E-Sports Prediction Tool\href{https://math10finalproject-k63yumzsdperqx7hdd2pww.streamlit.app/}{[Live Demo]}}{Nov.2021 - Dec.2021}{}{}
            \item {Trained Keras-based binary classification models to predict e-sports match outcomes using gameplay statistics from the first 10 minutes.}
            \item{Built a Streamlit web application to visualize predictions and display interactive game insights.}
        \end{rSubsection}
    \end{rSection}

    \begin{rSection}{Skills}
	\begin{itemize}
	    \item Programming Languages: Dart, JavaScript, HTML, CSS, python, C++
        \item Frameworks/Libraries: PyTorch, Numpy, Flutter, Riverpod, React, Node.js, Express.js ,SQL
        \item Development Tools: Git, Bash, Docker, NPM, Android Studio, Visual Studio Code
        
	\end{itemize}
		
	\end{rSection}
	
\end{document}

